% Repo: https://github.com/jack-alope/resume

\documentclass[letterpaper,11pt]{article}
%\pagestyle{empty}

\usepackage[utf8]{inputenc}
\usepackage[a4paper, portrait, margin=.5in, top=.6in, bottom=.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\usepackage{lastpage}
\usepackage[lastpage,user]{zref}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\rfoot{\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\cfoot{}
\lfoot{Jack F. Murphy}
\renewcommand{\footrulewidth}{0.4pt}

\usepackage{tabularx}

% -------------- Section Header Style ----------------------------
\titleformat*{\section}{\bfseries\Large\titlerule\vspace{-17pt}}
% ----------------------------------------------------------------

% -------------= Items Header Style -------------------------------
\newcommand{\itemHeadings}[4]{
    \begin{tabularx}{\textwidth} {>{\hsize=.65\textwidth\raggedright\arraybackslash}X 
   >{\raggedleft\arraybackslash}X}
      #1 & \small#2 \\
      #3 & \small#4
    \end{tabularx}
    \\
}

\newcommand{\itemitems}[1]{
    \begin{tabularx}{\textwidth} {>{\raggedleft\arraybackslash}X >{\hsize=.95\textwidth\raggedright\arraybackslash}X}
      &- \small#1 \\
    \end{tabularx}
    \\
}

\newcommand{\projHeadings}[2]{
    \begin{tabularx}{\textwidth} {>{\hsize=.7\textwidth\raggedright\arraybackslash}X 
   >{\raggedleft\arraybackslash}X}
      #1 & \small#2 \\
    \end{tabularx}
    \\
}

\newcommand{\projH}[1]{
    \begin{tabularx}{\textwidth} {>{\hsize=\textwidth\raggedright\arraybackslash}X}
      #1 \\
    \end{tabularx}
    \\
}

\newcommand{\projitems}[1]{
    \begin{tabularx}{\textwidth} {>{\raggedleft\arraybackslash}X | >{\hsize=.95\textwidth\raggedright\arraybackslash}X}
      & \small#1 \\
    \end{tabularx}
    \\
    \vspace{5pt}
}
% -----------------------------------------------------------------

% ------------- Heading Style -------------------------------------
\newcommand{\heading}[3]{
    \hspace{-15mm}
    \begin{tabular}{p{.4\textwidth} >{\raggedleft}p{.57\textwidth}}
        \textbf{\Huge{#1}}\vspace{5mm} & #2 $|$ #3 \\
    \end{tabular}
}
% -----------------------------------------------------------------

\newcommand{\sect}[1]{
    \vspace{-.4em}
    \section*{#1}
    \vspace{-3.5mm}
}

\begin{document}

% -------- Heading -------------------------------------------------------------
\heading
    {Jack F. Murphy}
    %{email: jack@mrph.dev}
    {jfm65@cam.ac.uk}
    {\href{https://jack.engineering}{https://jack.engineering}}
% ------------------------------------------------------------------------------

% ----------- Research Interests ------------------------------------------------------
%\section*{Research Interests}
\noindent
\vspace{0cm}
% --------------------------------------------------------------------------------------

% ----------- Education --------------------------------------------------------
\sect{Education}
    \itemHeadings
        {\textbf{The University of Cambridge}}
        {\textbf{October 2022 - present}}
        {\hspace{5pt}\emph{PhD in Engineering, Bioengineering}}
        {Cambridge, UK}
        %\itemitems
        %    {Thesis: Biomimetic, electroactive heart-on-a-chip platform. }
    \itemHeadings
        {\textbf{Trinity College Dublin}}
        {\textbf{September 2018 - May 2022}}
        %{\hspace{5pt}\emph{B.A.I in Biomedical Engineering, First Class Honours}}
        {\hspace{5pt}\emph{Baccalaureus in Arte Ingeniaria (B.A.I), Biomedical Engineering}}
        {Dublin, IE}
        \itemitems
            {First Class Honours}
        \itemitems
            {Thesis: 'Metabiomaterial: Multi-layed 3D immunomodulating patch'}
    % \itemHeadings
    %     {\textbf{The High School for Math, Science, and Engineering}}
    %     {\textbf{September 2014 - June 2018}}
    %     {\hspace{5pt}\emph{New York Regents Diploma, Advanced Designation with Honors}}
    %     {New York City, USA}
    %     \itemitems
    %         {Community Service and Mastery in Mathematics Distinctions}

% ------------------------------------------------------------------------------

% ----------- Publications ----------------------------------------------------------
\sect{Publications}
    \projHeadings{\textbf{Journal Articles}}{}
    	\itemitems
    		{J.F.Murphy \emph{et al. Bio-Design and Manufacturing.} (2024)} 
    	\itemitems
    		{Y.Pan \emph{et al. Cell Reports Physical Science.} \href{https://doi.org/10.1016/j.xcrp.2024.101930}{doi:10.1016/j.xcrp.2024.101930} (2024)} 
    	\itemitems
    		{J.F.Murphy \emph{et al. Computer Methods and Programs in Biomedicine Update} \href{https://doi.org/10.1016/j.cmpbup.2023.100107}{10.1016/j.cmpbup.2023.100107} (2023)}
        \itemitems
            {J.F. Murphy \emph{et al., Stem Cell Research and Therapy.} \href{https://doi.org/10.1186/s13287-019-1486-4}{doi:10.1186/s13287-019-1486-4} (2019)}
        \itemitems
            {J. Mayourian \emph{et al., Circulation Research.} \href{https://doi.org/10.1161/CIRCRESAHA.118.312420}{doi:10.1161/CIRCRESAHA.118.312420} (2018)}
    \projHeadings{\textbf{Book Chapters}}{}
        \itemitems
            {I. C. Turnbull \emph{et al., Methods in Molecular Biology.} \href{https://doi.org/10.1007/978-1-4939-8597-5\_11}{doi:10.1007/978-1-4939-8597-5\_11} (2018)}
    \projHeadings{\textbf{Conference Abstracts}}{}
	    \itemitems
	    	{J.F. Murphy \emph{et al. BioMedEng24.} (2024)}
	    \itemitems
	    	{J.F.Murphy \emph{et al. TERMIS World Congress 2024}}
        \itemitems
            {J.F. Murphy \emph{et al., Biomedical Engineering Society Annual Meeting.} (2019)}
        \itemitems
            {S.I. Salazar \emph{et al., New York Academy of Sciences.} (2019)}
        \itemitems
            {J.F. Murphy \emph{et al., American Heart Association Scientific Sessions.} (2018)}
        \itemitems
            {I.C. Turnbull \emph{et al., International Society for Stem Cell Research.} (2018)}
        \itemitems
            {J.F. Murphy \emph{et al, New York City Science and Engineering Fair.} (2018)}
    
% -----------------------------------------------------------------------------------

% ----------- Research Experience ---------------------------------------------------
\sect{Research Experience}
    \itemHeadings
        {\textbf{Monaghan Lab, Trinity Centre for Bioengineering}}
        {\textbf{September 2018 - May 2022}}
        {Research Assistant}
        {Dublin, IE}
        \itemitems
            {Characterised a novel biomaterial's mechanical and physiochemical properties through tensile testing, ELISA assays, FTIR analysis, mass spectroscopy, flow cytometry, and contact angle assessment.}
        \itemitems
            {Provided expertise to PhD students on 3D design and printing, induced-pluripotent stem cell culture and differentiation, and engineered cardiac tissue fabrication techniques. }
        \itemitems
            {Key exchange point of international collaboration between the Costa Lab (NYC) and the Monaghan Lab (Dublin). Focused on adapting an engineered cardiac tissue bioreactor for use with a novel pacing system.}
        \itemitems
            {Performed histological staining and analysis of tissue explants with polarized light microscopy to characterize fibrotic encapsulation around next-generation silicone implants. }
        \itemitems
            {Carried out in-depth image analysis using threshold segmentation and region-of-interest normalization.}
        \itemitems
            {Developed a setup to determine propagation of electric pulses across biomaterial bridge between fresh muscle tissues ex vivo.}
    \itemHeadings
        {\textbf{Turnbull Lab, Icahn School of Medicine at Mount Sinai}}
        {\textbf{June 2021 - September 2021}}
        {Research Assistant}
        {New York City, USA}
        \itemitems
            {Developed Rian\'u, a web application capable of tracking and analyzing multiple cardiac tissues simultaneously.}
        \itemitems
            {Modified the existing tissue recording setup to record multiple tissues in a single frame.}
    \itemHeadings
          {\textbf{Costa Lab, Icahn School of Medicine at Mount Sinai}}
          {\textbf{March 2017 - September 2020}}
          {Research Assistant}
          {New York City, USA}
        \itemitems
            {Maintained induced-pluripotent stem cells (iPSCs), mesenchymal stem cells, and cardiac stem cells in culture.}
        \itemitems
            {Differentiated iPSCs into cardiomyocytes and fabricated 3D human engineered cardiac tissues. Used engineered tissue as a testing platform for various drug- and cell-based therapies for cardiac regeneration.}
        \itemitems
            {Used existing LabVIEW and MATLAB software to collect and analyze data on cardiac function.}
        \itemitems
            {Designed and printed 3D accessories to help with the data collection process.}
    \itemHeadings
        {\textbf{Dean Lab, Columbia University}}
        {\textbf{June 2017 - December 2017}}
        {Lab Intern}
        {New York City, USA}
        \itemitems
            {Exfoliated graphite to get monolayers of graphene and used a bright field microscope to  record locations.}
        \itemitems
            {Created a graphene device insulated by boron nitride and used atomic force microscopy to identify imperfections.}
% -----------------------------------------------------------------------------------
\sect{Teaching Experience}
	\itemHeadings
		{\textbf{Department of Engineering, University of Cambridge}}
		{\textbf{October 2023 - January 2024}}
		{M1P Demonstrator}
		{Cambridge, UK}
	\itemHeadings
		{\textbf{Department of Engineering, University of Cambridge}}
		{\textbf{October 2022 - December 2022}}
		{CAD Demonstrator}
		{Cambridge, UK}
    \itemHeadings
        {\textbf{Voluntary Tuition Program, Trinity College Dublin}}
        {\textbf{September 2018 - May 2019}}
        {Maths Tutor}
        {Dublin, IE}
        \itemitems
            {Met with a primary school student each week to aid them in their understanding of maths.}
    \itemHeadings
        {\textbf{Center for Excellence in Youth Education at Mount Sinai}}
        {\textbf{September 2016 – June 2018}}
        {Research Scholar}
        {New York City, USA}
        \itemitems
            {Guided middle school students through laboratory dissections of the heart, eye, and kidney.}
        \itemitems
            {Provided guidance and advice on the New York City high school application process.}
% ----------- Projects ---------------------------------------------------  
\sect{Open Source Projects}
    \projH{\textbf{Rian\'u:} Multi-tissue tracking software for increased throughput of engineered cardiac tissue screening}{\hspace*{.5cm}\url{https://rianu.mrph.dev}}\\
        \itemitems
            {Identified a bottleneck in existing engineered cardiac tissue analysis software.}
        \itemitems
            {Created a web application capable of tracking and analyzing multiple engineered cardiac tissues simultaneously.}
        \itemitems
            {Validated this software against existing software and provided detailed documentation for its use.}
        \itemitems
            {Actively maintain this software and will release it open-source under the BSD 3-Clause License upon publication.}
    %\projH{\textbf{Web Design}}
    %    \itemitems
       %     {Developed my personal portfolio website that automatically updates citation counts by paper DOI.}
        %\itemitems
        %    {Released the custom theme open-source \href{https://themes.gohugo.io/themes/sourgough-starter/}{(\small themes.gohugo.io/themes/sourgough-starter}).}
        %\itemitems
        %    {Created websites for various projects, other students, a student society, a band, and for software documentation.}
    \projH{\textbf{doi3bib}: A website that converts DOI's into \LaTeX~compatible bibtex entries}{\hspace*{.5cm}\url{https://doi3bib.com}}\\
        \itemitems
            {A simple serverless web app that returns latex compatible bibtex entries when supplied with a DOI or PMID.}
        \itemitems
            {Obtains bibtex entries for doi.org or crossref.org and parses them to make sure they are compatible with \LaTeX.}
% ------------------------------------------------------------------------


% ----------- Volunteer Experience ---------------------------------------------------
%\section*{Volunteer Experience}
%    \itemHeadings
%          {\textbf{Life Rolls on Foundation}}
%          {August 2018 - August 2019}
%          {Mid-Level Water Volunteer}
%          {New York City, USA}
%        \itemitems
%            {Annual event to give people living with paralysis the opportunity to surf by helping position them on the board, carry them out past the wave breaks, and then guide their path on the way back in.}
%    \itemHeadings
%          {\textbf{Voluntary Tuition Program}}
%          {September 2018 - May 2019}
%          {Maths Tutor}
%          {Dublin, Ireland}
%        \itemitems
%            {Met with a primary school student each week to aid them in their understanding of geometry.} 
% -----------------------------------------------------------------------------------

\sect{Further Information}
    \projHeadings{\textbf{Awards}}{}
    	\itemitems
    		{Sports Personality of the Year, Univerisity of Cambridge (2024)}
        \itemitems
            {W.D Armstrong Studentship, School of Technology, University of Cambridge (2022 - 2026)}
        \itemitems
            {Honorary Robert Gardiner Memorial Scholarship, University of Cambridge (2022)}
        \itemitems
            {Book Prize, Department of Engineering, Trinity College Dublin (2019, 2020, 2021)}
        \itemitems
            {New York City Science and Engineering Fair (NYCSEF) Finalist, Second Award (2018)}
        \itemitems
            {Frank W. and Jane J. Stahl Memorial Award for Technical Excellence, NYCSEF (2018)}
        \itemitems
            {Naval Science Award, Office of Naval Research, NYCSEF (2018)}
    \projHeadings{\textbf{Positions}}{}
    	\itemitems
    		{Assistant Captain, Cambridge University Blues Men's Ice Hockey Team (2024 - present)}
    	\itemitems
    		{Club Secretary, Cambridge University Ice Hockey Club (2024 - present)}
    \projHeadings{\textbf{Memberships}}{}
        \itemitems
            {Engineers Ireland, Student Membership (2018 - 2022)}
    \projHeadings{\textbf{Citizenships}}{}
        \itemitems
            {Republic of Ireland}
        \itemitems
            {United States of America}
    \projHeadings{\textbf{Sports}}{}
        \itemitems
            {Cambridge University Blues Men's Ice Hockey Team, Defenceman (2022 - present)}
    \projHeadings{\textbf{Skills}}{}
        \itemitems
            {Programming: C++, Docker, Python including OpenCV, JS, Web design, MATLAB}
        \itemitems
            {CAD: Solidworks, Autodesk Fusion 360, Revit and Inventor, OpenSCAD}
        \itemitems
            {Microscopy: Tissue staining, sectioning, and mounting, Confocal, Polarized Light}
        \itemitems
            {Data Analysis: ImageJ/FIJI, Graphpad Prism, R, Excel}
        \itemitems
            {Office: \LaTeX, EndNote 20, Microsoft Word}
            
% \sect{References}
% \begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
%     \textbf{Kevin D. Costa} \newline 
%     Associate Professor of Medicine, Cardiology \newline
%     Icahn School of Medicine at Mount Sinai \newline
%     kevin.costa@mssm.edu
%     & 
%     \textbf{Michael G. Monaghan} \newline
%     Ussher Assistant Professor, Biomedical Engineering \newline
%     Trinity College Dublin \newline
%     monaghmi@tcd.ie
%     \\ \vspace*{.2cm}

%     \textbf{Irene C. Turnbull} \newline
%     Assistant Professor of Medicine, Cardiology \newline
%     Icahn School of Medicine at Mount Sinai \newline
%     irene.turnbull@mssm.edu
    
%     \\
% \end{tabular}
\end{document}
